---
title: "Assignment 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(dplyr)
library(lubridate)
library(surveillance)
library(shiny)
source('./R/glrpoisApp.R')
source('./R/surv.ds.convert.R')

#source('./R/Prep_raw_data.R')

```


## Import Data

This dataset (a1) contains the number of people visiting Emergency Departments in Brooklyn, NY for diarrhea.

```{r}
a1 <- readRDS('./Data/u5_diarrhea_brooklyn.rds')
```


## Plot the time series for Children under 5
```{r}

```

## Harmonic regression

Our goal is to establish a prospective abberation detective algorithm for diarrhea in kids. Let's first focus on the period before the pandemic, which is subset and saved in data frame a2 below:

```{r}
a2 <- a1[a1$date<'2020-03-01',]

a2 <- a2[order(a2$date),] #ensure it is sorted by date

a2$index <- 1: nrow(a2) # create an index variable 1:number of rows in a2

a2$day_of_week <- as.factor(weekdays(a2$date))
```

Create the harmonic variables you need for a harmonic regression. Remember, this is daily data

```{r}

```

Fit your Poisson regression model

```{r}

```

Plot your output observed and fitted values

```{r}

```

Next fit a robust harmonic regression

```{r}

```

Generate the fitted values and prediction intervals

```{r}

```

Plot the predictions

```{r}

```

## Now develop a seasonal CUSUM for the post-pandemic period, for weekly data

```{r}
a3 <- readRDS( './Data/weekly_u5_diarrhea_brooklyn_pandemic.rds')


#Create a version of the time series that is missing for 4th quarter of 2021
a3$cases_train <- a3$cases
a3$cases_train[a3$week.date>='2021-10-01'] <- NA

a3 <- a3[order(a3$week.date),]

a3$index <- 1:nrow(a3)
```

Fit a Poisson regression to the weekly data through the end of Q3 2021. (You can use variale 'cases_train' for model fitting) Remember this is weekly data now.

```{r}

```

Now use the glrpois App to try out a cusum-type approach with these data. 

```{r}
glrpois_App(a3, datevar='week.date', casevar='cases', n.weeks.train=79)
```




